---
title: "MIMIC-III Lab Events Item ID"
author: "<h3><p>Yuzhe (Vanessa) You vyou@umich.edu</p></h3>  <h3><p>Ziyuan Sun ziyuans@umich.edu</p></h3> <h3><p> Jessica Wild<h3><p>"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
subtitle: <h2><u>Winter 2019, SOCR-MDP</u></h2>
---

```{r message=F, warning=F}
# Data preparation
library('psych')          # descriptive stats

# Plots and tables
library('knitr')          # knitting Rmd to HTML; kable() function
library('kableExtra')     # extra formating options for knitr tables
library('ggplot2')        # 2d plotting
library('ggpubr')         # extra formatting options for ggplot
```

**Random Seed Set**
```{r message=F, warning=F}
set.seed(123456)
```

# Extracting the data
We first calculated the total number of distinct itemids:

`SELECT count(distinct itemid) FROM labevents as items_count`

And the result gives us `726`, showing us that there are 726 itemids from labevents.

Then we calculated the 25 most common itemids:

`SELECT itemid, count(itemid) FROM labevents GROUP by itemid Order by count(*) LIMIT 25`

Which gives us the table:

```{r eval=T, message=F, warning=F}
frequency_data <- read.csv('count.csv')
str(frequency_data)
```

```{r eval=T, message=F, warning=F}
kable(head(frequency_data), caption="The 25 most common itemids") %>%
kable_styling(bootstrap_options='striped')
```

Then by finding those 25 itemids in the corresponding d_labitems, we see what they map to:

`SELECT * FROM d_labitems WHERE itemid = 51221 
OR itemid = 50971
OR itemid = 50983
OR itemid = 50912
OR itemid = 50902
OR itemid = 51006
OR itemid = 50882
OR itemid = 51265
OR itemid = 50868
OR itemid = 51301
OR itemid = 51222
OR itemid = 50931
OR itemid = 51249
OR itemid = 51279
`

```{r eval=T, message=F, warning=F}
itemid_data <- read.csv('25 itemids.csv')
str(itemid_data)
```

```{r eval=T, message=F, warning=F}
kable(head(itemid_data), caption="The 25 most common itemids") %>%
kable_styling(bootstrap_options='striped')
```
