---
title: "MIMIC-III Lab Events Item ID"
author: "<h3><p>Yuzhe (Vanessa) You vyou@umich.edu</p></h3>  <h3><p>Ziyuan Sun ziyuans@umich.edu</p></h3> <h3><p> Jessica Wild jesswild@umich.edu<h3><p>"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
subtitle: <h2><u>Winter 2019, SOCR-MDP</u></h2>
---

```{r message=F, warning=F}
# Data preparation
library('psych')          # descriptive stats

# Plots and tables
library('knitr')          # knitting Rmd to HTML; kable() function
library('kableExtra')     # extra formating options for knitr tables
library('ggplot2')        # 2d plotting
library('ggpubr')         # extra formatting options for ggplot
```

**Random Seed Set**
```{r message=F, warning=F}
set.seed(123456)
```

# Extracting the data
We first calculated the total number of distinct itemids:

`SELECT count(distinct itemid) FROM labevents as items_count`

And the result gives us `726`, showing us that there are 726 itemids from labevents.

Then we calculated the 25 most common itemids:

`SELECT itemid, count(itemid) FROM labevents GROUP by itemid Order by count(*) LIMIT 25`

Which gives us the table:

```{r eval=T, message=F, warning=F}
frequency_data <- read.csv('count.csv')
str(frequency_data)
```

```{r eval=T, message=F, warning=F}
kable(frequency_data, caption="The 25 most common itemids") %>%
kable_styling(bootstrap_options='striped')
```

Then by finding those 25 itemids in the corresponding d_labitems, we see what they map to:

`SELECT * FROM d_labitems WHERE itemid = 51221 
OR itemid = 50971
OR itemid = 50983
OR itemid = 50912
OR itemid = 50902
OR itemid = 51006
OR itemid = 50882
OR itemid = 51265
OR itemid = 50868
OR itemid = 51301
OR itemid = 51222
OR itemid = 50931
OR itemid = 51249
OR itemid = 51279
`
```{r eval=T, message=F, warning=F}
itemid_data <- read.csv('25 itemids.csv')
str(itemid_data)
```

```{r eval=T, message=F, warning=F}
kable(itemid_data, caption="The 25 most common itemids") %>%
kable_styling(bootstrap_options='striped')
```

Since each itemid stands for a distinct lab test, we determined that none of the itemids are likely to be redundant, and so there was no need to merge any of them.

#Plots for itemids

Here we made a bar chart that shows the frequency of the 25 most common itemids:

```{r eval=T, message=F, warning=F,fig.width=20,fig.height=10}
barplot(frequency_data$count,names.arg=frequency_data$itemid,xlim=c(1,25),ylim=c(0,10^6),xlab='item id',main='the barplot for most common 25 itemids')
```

And a pie chart that shows the frequency of all itemids:

```{r eval=T, message=F, warning=F,fig.width=10,fig.height=10}
frequency_all_data <- read.csv('count_all.csv')
de<-data.frame(itemid='others',count=sum(frequency_all_data$count[26:726]))
new_frequency<-rbind(frequency_all_data[1:25,],de)
pie(new_frequency$count,labels =new_frequency$itemid,main='pie chart for major itemids')
```

#Bar Charts for itemids

To visualize the results of the most common tests, we can make bar charts displaying the results (normal vs abnormal) for each of the top five itemids


```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_51221 <- read.csv('51221.csv')

for (i in 1:nrow(data_51221)) {
  if (data_51221$flag[i] == "") {
    data_51221$flag_1[i] <- "normal"
  }
  else {
    data_51221$flag_1[i] <- "abnormal"
  }
}
  
barplot(prop.table(table(data_51221$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_50971 <- read.csv('50971.csv')

for (i in 1:nrow(data_50971)) {
  if (data_50971$flag[i] == "") {
    data_50971$flag_1[i] <- "normal"
  }
  else {
    data_50971$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_50971$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_50983 <- read.csv('50983.csv')

for (i in 1:nrow(data_50983)) {
  if (data_50983$flag[i] == "") {
    data_50983$flag_1[i] <- "normal"
  }
  else {
    data_50983$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_50983$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_50912 <- read.csv('50912.csv')

for (i in 1:nrow(data_50912)) {
  if (data_50912$flag[i] == "") {
    data_50912$flag_1[i] <- "normal"
  }
  else {
    data_50912$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_50912$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_50902 <- read.csv('50902.csv')

for (i in 1:nrow(data_50902)) {
  if (data_50902$flag[i] == "") {
    data_50902$flag_1[i] <- "normal"
  }
  else {
    data_50902$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_50902$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_51006 <- read.csv('51006.csv')

for (i in 1:nrow(data_51006)) {
  if (data_51006$flag[i] == "") {
    data_51006$flag_1[i] <- "normal"
  }
  else {
    data_51006$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_51006$flag_1)))
```

```{r eval=T, message=F, warning=F,fig.width=3,fig.height=3}
data_50882 <- read.csv('50882.csv')

for (i in 1:nrow(data_50882)) {
  if (data_50882$flag[i] == "") {
    data_50882$flag_1[i] <- "normal"
  }
  else {
    data_50882$flag_1[i] <- "abnormal"
  }
}

barplot(prop.table(table(data_50882$flag_1)))
```
